---
title: "Project#1"
output: html_document
---

## Read data into R
```{r}
BodyFat = read.csv("/Users/irenecho/Desktop/stat 333/project/BodyFat.csv")
attach(BodyFat)
dim(BodyFat)
```

```{r}
colnames(BodyFat)
```

## Analyzing Raw Data
```{r}
head(BodyFat) #Look at the first few data
tail(BodyFat) #Look at the last few data
```

Weight and height are both measured in inches

Neck, chest, abdomen are measured in ml (more precise)

```{r}
summary(BodyFat)
```

## Visualizing Data
```{r}
par(mfrow=c(3,2)) #create a matrix of 3X2 filled by row
par(mgp=c(1.8,.0,0), mar=c(3,3,1,1)) 
hist(BodyFat$BODYFAT, breaks = 30,
     main="Histogram of Body Fat %", xlab = "Body Fat %")
hist(BodyFat$DENSITY, breaks = 30,
     main="Histogram of Density", xlab = "Density(Inches)")
hist(BodyFat$AGE, breaks = 30,
     main="Histogram of Age", xlab = "Age(years)")
hist(BodyFat$WEIGHT, breaks = 30,
     main="Histogram of Weight", xlab = "Weight(Ibs)")
hist(BodyFat$HEIGHT, breaks = 30,
     main="Histogram of Height", xlab = "Height(Inches)")
```

## Data Cleaning(Subset of Data)
```{r}
BodyFat[BodyFat$BODYFAT>=45|BodyFat$BODYFAT<3,]
BodyFat[BodyFat$HEIGHT<40,]
BodyFat[BodyFat$WEIGHT>300,]
BodyFat[BodyFat$NECK>45,]
BodyFat<- BodyFat[-c(172,182,216,42,39),]
summary(BodyFat)
```

## Statistical Modeling and Analysis
```{r}
plot(BodyFat$AGE,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Age(yrs)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Age")

plot(BodyFat$WEIGHT,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Weight(Ibs)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Weight")

plot(BodyFat$HEIGHT,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Height(Inches)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Height")
  
plot(BodyFat$ADIPOSITY,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Adiposity(bmi)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Adiposity")

plot(BodyFat$NECK,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Neck(cm)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Neck")
```


```{r}
plot(BodyFat$NECK,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Neck(cm)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Neck")
lmmodel= lm(BODYFAT ~ NECK  )
abline(lmmodel, col="blue", lwd=5)
summary(lmmodel)
```
explains about 24.16% of variation in body fat

```{r}
plot(BodyFat$ADIPOSITY,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Adiposity(bmi)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Adiposity")
lmmodel= lm(BODYFAT ~ ADIPOSITY  )
abline(lmmodel, col="blue", lwd=5)
summary(lmmodel)
```
explains about 53% of variation in body fat

```{r}
plot(BodyFat$HEIGHT,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Height(Inches)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Height")
lmmodel= lm(BODYFAT ~ HEIGHT  )
abline(lmmodel, col="blue", lwd=5)
summary(lmmodel)
```
explains about 0.79% of variation in body fat

```{r}
plot(BodyFat$WEIGHT,BodyFat$BODYFAT,pch=19, cex=1.2, cex.lab=1.5, cex.main=1.5,
     xlab="Weight(Ibs)", ylab="Body Fat %", main="Scatterplot of Body Fat % and Weight")
lmmodel= lm(BODYFAT ~ WEIGHT)
abline(lmmodel, col="blue", lwd=5)
summary(lmmodel)
```
explains about 37.6% of variation in body fat

```{r}
lmmodel= lm(BODYFAT ~WEIGHT+ NECK + ADIPOSITY)
summary(lmmodel)
```


reject the null that they are not related


## Diagnostics
Residual(homoskecidicity, no linear trend)

QQ Plot(linearity)

outlier/influential points(leverage values, cook's distance= no trend, no influential point)



